A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-17 04_Severity_MetaAnalysis.Rmd
add library(gam)

Load libraries and data  
```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable)

>>>>

Load libraries and data  
```{r MEsummary_Libraries2, echo=TRUE,results='hide'}
if (!require("pacman"))
   install.packages("pacman")
pacman::p_load(tidyverse,
               kableExtra,
               bomrang,
               RColorBrewer,
               metafor,
               here,
               netmeta,
               multcomp,
               dplyr,
               flextable,
               gam)
